Weighted Model Counting with Conditional Weights for Bayesian Networks

### 2020-12-01 paper2/paper.tex
All kinds of minor changes

\section{Boolean Algebras, Power Sets, and Propositional
  Logic} \label{sec:prelims}

@@

% TODO: add a link to CUDD
We also consider the space of all functions from any Boolean algebra to
$\mathbb{R}_{\ge 0}$ together with some operations on those functions. They will
be instrumental in defining WMC as a measure in \cref{sec:wmc_as_measure} and
can be efficiently represented using ADDs. Furthermore, all of the operations
are supported by CUDD package that is used by ADDMC for ADD manipulation
\cite{DBLP:conf/aaai/DudekPV20}. The definitions of multiplication and
projection are as defined by Dudek \etal{}~\shortcite{DBLP:conf/aaai/DudekPV20},
while others are new.

@@

\section{Encoding Bayesian Networks Using Conditional Weights} \label{sec:bns}
% TODO: make it clear which parts of the encoding are not new
% TODO: rewrite the encoding without using an algorithm (look into the feedback
% of reviewer #5 and someone before him)
% TODO: explain/prove why it's impossible for the all-zero encoding to represent
% the last value (a.k.a. the -implicit flag)

@@

\section{Experimental Comparison} \label{sec:experiments}
% TODO: stacked bar charts: 1) mention that the error bars denote 0.1 * standard
% deviation
% 2) and that only successfully run instances are included
% 3) and that the top error bar relates only to inference (and not the sum of
% the two)
% TODO: note: I'm unable to replicate the experiments from bklm. This could be
% due to two reasons:
% 1) I'm measuring running time rather than compiled structure size <- more
% likely
% 2) I'm not using the -implicit flag.
% TODO: We use Ace to compile the BN together with its evidence (as opposed to
% compiling just the BN and using evidence during inference) as this more
% closely resembles the behaviour of ADDMC
% TODO: we run cd05 only with dtBnMinfill, as that's the more commonly used
% setting (although another one was used as well)
% TODO: The -implicit flag of bklm16 cannot be used because even a small
% Bayesian network with seven independent binary variables with 0.1/0.9
% probabilities is already big enough to drive the scaling factor down to zero.
% The last step of this encoding is a multiplication of a huge number (on the
% order of 10^30 for some of the smaller DQMR instances) by a number
% equivalently close to zero (so that their product lands in the interval [0,
% 1]). Thus, we disable this flag (thus making the algorithm slower but
% correct).
% TODO: the legacy mode encoding of bklm16 also runs c2d (as packaged with Ace)
% TODO: query-dnnf: http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html
% TODO: bn2cnf http://www.cril.univ-artois.fr/KC/bn2cnf.html
% TODO: Note that our encoder was implemented in Python with no concern for
% efficiency, so encoding could easily be improved by one or two orders of
% magnitude.
% TODO: Python, Java, gcc versions (maybe also all the software that I'm using
% (e.g., bn2cnf, Cachet))
% TODO: 85% is as recommended in the README of Ace (might have to go lower than that)
% TODO: for each encoding, mention:
% 1) software
% 2) encoding options
% 3) additional data processing
% 4) inference options

>>>>

\section{Boolean Algebras and Propositional Logic} \label{sec:prelims}

@@

% TODO: explain what CUDD is
We also consider the space of all functions from any Boolean algebra to
$\mathbb{R}_{\ge 0}$ together with some operations on those functions. They will
be instrumental in defining WMC as a measure in \cref{sec:wmc_as_measure} and
can be efficiently represented using ADDs. Furthermore, all of the operations
are supported by CUDD package that is used by ADDMC for ADD manipulation
\cite{DBLP:conf/aaai/DudekPV20}. The definitions of multiplication and
projection are as defined by Dudek \etal{}~\shortcite{DBLP:conf/aaai/DudekPV20},
while others are new.

@@

\section{Example: Bayesian Networks} \label{sec:bns}
% TODO: make it clear which parts of the encoding are not new
% TODO: rewrite the encoding without using an algorithm (look into the feedback
% of reviewer #5 and someone before him)
% TODO: explain/prove why it's impossible for the all-zero encoding to represent
% the last value (a.k.a. the -implicit flag)

@@

\section{Experimental Comparison} \label{sec:experiments}
% TODO: stacked bar charts: 1) mention that the error bars denote 0.1 * standard
% deviation
% 2) and that only successfully run instances are included
% 3) and that the top error bar relates only to inference (and not the sum of
% the two)
% TODO: note: I'm unable to replicate the experiments from bklm. This could be
% due to two reasons:
% 1) I'm measuring running time rather than compiled structure size <- more
% likely
% 2) I'm not using the -implicit flag.
% TODO: We use Ace to compile the BN together with its evidence (as opposed to
% compiling just the BN and using evidence during inference) as this more
% closely resembles the behaviour of ADDMC
% TODO: we run cd05 only with dtBnMinfill, as that's the more commonly used
% setting (although another one was used as well)
% TODO: The -implicit flag of bklm16 cannot be used because even a small
% Bayesian network with seven independent binary variables with 0.1/0.9
% probabilities is already big enough to drive the scaling factor down to zero.
% The last step of this encoding is a multiplication of a huge number (on the
% order of 10^30 for some of the smaller DQMR instances) by a number
% equivalently close to zero (so that their product lands in the interval [0,
% 1]). Thus, we disable this flag (thus making the algorithm slower but
% correct).
% TODO: the legacy mode encoding of bklm16 also runs c2d (as packaged with Ace)
% TODO: Note that our encoder was implemented in Python with no concern for
% efficiency, so encoding could easily be improved by one or two orders of
% magnitude.
% TODO: Python, Java, gcc versions (maybe also all the software that I'm using
% (e.g., bn2cnf, Cachet))
% TODO: 85% is as recommended in the README of Ace (might have to go lower than that)
% TODO: for each encoding, mention:
% 1) software
% 2) encoding options
% 3) additional data processing
% 4) inference options

TODO: Things I will need to mention:
\begin{itemize}
\item
  \texttt{query-dnnf}\footnote{\url{http://www.cril.univ-artois.fr/kc/d-DNNF-reasoner.html}}
\item
  \texttt{bn2cnf}\footnote{\url{http://www.cril.univ-artois.fr/KC/bn2cnf.html}}
  and \texttt{bklm16} \cite{DBLP:conf/ecai/BartKLM16}
\end{itemize}
